### 2019-03-01 sections/language.tex
fixed minor nits in calculus section

\label{sub:pretasks}
The grammar in \cref{fig:task-grammar} specifies the syntactic category of \emph{pretasks}.
Pretasks are tasks that have unevaluated subexpressions with respect to the host language.
Who expressions are evaluated will be discussed in \cref{sec:evaluation}.
Each pretask will be discussed in more detail in the following subsections.
We use open symbols ($\Edit, \Enter, \Next, \Xor$) for tasks that require user input, and closed symbols ($\Update, \Then, \Or$) for tasks that can be evaluated without user input.

@@

Editors that hold an expression $e : \tau$ have type $\Task \tau$.
Empty editors are annotated with a type in order to ensure type safety.
Without that it would be possible to change the type of an editor, by clearing it and filling it with a value of different type.

@@

Changes to a shared editor are immediately visible to all shared editors watching the same reference.
Imagine two users, Marco and Christopher, both watching shared editors of the same coordinate.
The editors are visualised as a pin on a map.
When Marco moves his pin, he updates the value of the shared editor, thereby changing the value of the reference.
This change is immediately reflected on Christopher's screen: The pin changes its position on his map.
This way Marco and Christopher can work together to edit the same information.

>>>>

\label{sub:pretasks}
The grammar in \cref{fig:task-grammar} specifies the syntactic category of \emph{pretasks}.
Pretasks are tasks that have unevaluated subexpressions with respect to the host language.
How expressions are evaluated will be discussed in \cref{sec:evaluation}.
Each pretask will be discussed in more detail in the following subsections.
We use open symbols ($\Edit, \Enter, \Next, \Xor$) for tasks that require user input, and closed symbols ($\Update, \Then, \Or$) for tasks that can be evaluated without user input.

@@

Editors that hold an expression $e : \tau$ have type $\Task \tau$.
Empty editors are annotated with a type in order to ensure type safety.
Without type annotations, it would be possible to change the type of an editor, by clearing it and filling it with a value of different type.

@@

Changes to a shared editor are immediately visible to all shared editors watching the same reference.
Imagine two users, Marco and Christopher, both watching shared editors of the same coordinates.
The editors are visualised as a pin on a map.
When Marco moves his pin, he updates the value of the shared editor, thereby changing the value of the reference.
This change is immediately reflected on Christopher's screen: The pin changes its position on his map.
This way Marco and Christopher can work together to edit the same information.
